---
title: "Consumer Financial Protection Bureau complaints from March-December 2020"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: readable
---

Findings
==================
```{r setup, include=FALSE}
#load libraries
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(readxl)
library(writexl)
library(DT)
library(scales)
library(ggthemes)
library(esquisse)
library(shiny)
library(jsonlite)
library(maptools)
library(tidyr)
library(dplyr)
library(purrr)
library(leaflet)
library(plotly)
library(glue)
library(kableExtra)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
options(tigris_class = "sf")


#Import data
complaints <- readRDS("~/Downloads/github/consumer-complaints-gw/complaints.rds")

#Clean data
complaints <- complaints %>% 
  clean_names()

#Make a smaller table of most common complaints
condensed_products <- complaints %>% 
  filter(product %in% c("Credit reporting, credit repair services, or other personal consumer reports", 
                          "Debt collection", 
                          "Mortgage", 
                          "Credit card or prepaid card"))

#Making a dataset of most complained about states
condensed_states <- complaints %>% 
  filter(state %in% c("FL", 
                      "CA", 
                      "TX", 
                      "NY",
                      "GA", 
                      "PA", 
                      "IL", 
                      "NJ", 
                      "NC")) 

#Making a dataset of condensed products and states
condensed_p_s <- complaints %>% 
  filter(state %in% c("FL", 
                      "CA", 
                      "TX", 
                      "NY",
                      "GA", 
                      "PA", 
                      "IL", 
                      "NJ", 
                      "NC")) %>% 
filter(product %in% c("Credit reporting, credit repair services, or other personal consumer reports", 
                          "Debt collection", 
                          "Mortgage", 
                          "Credit card or prepaid card"))

#MAP SETUP 
# # Downloading the shapefile boundaries for states using tigris package
states <- states(cb=T)

#### STATE BY STATE SHADED MAP ####

grouped_states <- complaints %>% 
  group_by(state) %>%
  summarize(total=n()) 

# Tigris function GEO_JOIN to bring together 
states_merged_sb <- geo_join(states, grouped_states, "STUSPS", "state")

# MAKING THE MAP ####

# getting rid of rows with NA values
states_merged_sb <- subset(states_merged_sb, !is.na(total))
states_merged_sb$total <- as.integer(states_merged_sb$total)

# creating a color palette based on the number range in the total column
mypalette <- colorNumeric("Spectral", domain=states_merged_sb$total)
            
popup_sb <- paste0("Total complaints: ", as.character(states_merged_sb$total))
```

Column
-----------------------------------------------------------------------

### Total complaints, by state

```{r, fig.width=10, fig.height=7}

#MAP

leaflet() %>% 
  addTiles() %>% # <-- Base map
  setView(-98.483330, 38.712046, zoom = 4) %>% # <-- Zooming to Continental US
  addPolygons(data = states_merged_sb , # <-- Adding polygons to map
              fillColor = ~mypalette(states_merged_sb$total), 
              fillOpacity = 0.9, 
              weight = 0.2, 
              smoothFactor = 0.2,
              label=popup_sb, # <--- Hover popups
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = mypalette,    # <--- Adding a legend
            values = states_merged_sb$total,
            bins = 4,
            position = "bottomright", 
            title = "Total complaints", 
            labFormat = labelFormat(digits = 0)
  )

```

Row
-----------------------------------------------------------------------

### Most Common Complaints

```{r}

library(plotly)
fig <- plot_ly(
  x = c("Personal Consumer Reports", "Debt Collection", "Credit Card or Prepaid Card"),
  y = c(255748, 46088, 29128),
  name = "Most Common Complaints",
  type = "bar"
)
fig



#Most complained about product
complaints %>%
  count(product, sort = TRUE)

```

Row
-----------------------------------------------------------------------

### Lowest complaint rate

```{r}

valueBox("Student Loan Debt", icon="fa-pencil")

```

### Highest complaint rate

```{r}

valueBox("Personal Consumer Reports", icon="fa-money")

```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Companies that recieve the most complaints

```{r}

library(plotly)
fig <- plot_ly(
  x = c("Experian Information Solutions Inc.", "TRANSUNION INTERMEDIATE HOLDINGS, INC.", "EQUIFAX, INC.", "CAPITAL ONE FINANCIAL CORPORATION", "BANK OF AMERICA, NATIONAL ASSOCIATION"),
  y = c(81264, 77386, 70075, 8317, 8191),
  name = "Companies that receive the most complaints",
  type = "bar"
)
fig

complaints %>%
  count(company, sort = TRUE)

```

### Most complaints per state

```{r}

library(plotly)
fig <- plot_ly(
  x = c("FL", "CA", "TX", "NY", "GA", "PA", "IL", "NJ", "NC"),
  y = c(50449, 46721, 44504, 25445, 23881, 18380, 12732, 12643, 10878),
  name = "Most complaints per state",
  type = "bar"
)
fig

#Most complaints per state
complaints %>%
  count(state, sort = TRUE)
```

About
==================

The following data examines complaints the Consumer Financial Protection Bureau sends to companies for response. The complaints are published in the Consumer Complaint Database after the company responds, confirming a commercial relationship with the consumer, or after 15 days. 

The visualizations seen in the "Findings" tab seek to examine the most common consumer complaints, the companies that come up most frequently, and the states that appear most frequently in the data.

It is important to note the condensed data sizes for some of the graphs and charts, allowing for a less cluttered data table. 
